String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-08 2023-1-19/sections/introduction.tex
related work

\paragraph*{Related work} 
We discuss more related work about regular expressions with counting and real-world regular expressions in programming languages here.  
Determinism of regular expressions with counting was investigated in~\cite{GGM12,CL15}. Counting-set automata was proposed in~\cite{redos_lenka,HS+23} to enable fast matching of a subclass of regular expressions with counting.  Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regular expressions with counting.   Nevertheless, nonemptiness problem of these automata, which is the key for automata-based string constraint solving, was not considered in ~\cite{redos_lenka,HS+23,GKM23}.
Real-world regular expressions in programming languages include some features beyond classical regular expressions, e.g. the greedy/lazy Kleene star, capturing groups, and back references. Real-world regular expressions haven been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.

>>>>

\paragraph*{Related work} 
We discuss more related work about regular expressions with counting and real-world regular expressions in programming languages here.  
Determinism of regular expressions with counting was investigated in~\cite{GGM12,CL15}. Counting-set automata was proposed in~\cite{redos_lenka,HS+23} to enable fast matching of a subclass of regular expressions with counting.  Moreover, a variant of nondeterministic counter automata, called bit vector automata, was proposed recently in \cite{GKM23} to enable fast matching of a more expressive class of regular expressions with counting.   Nevertheless, nonemptiness problem of these automata was not considered in ~\cite{redos_lenka,HS+23,GKM23} and it is unclear whether these automata models can be used for solving string constraints with regex-counting and string-length.
Real-world regular expressions in programming languages include some features beyond classical regular expressions, e.g. the greedy/lazy Kleene star, capturing groups, and back references. Real-world regular expressions haven been addressed in symbolic execution of Javascript programs~\cite{LMK19} and string constraint solving \cite{CF+22}.
